---
title: "Initial Counts Draft 7"
author: "Ingrid Shu"
date: "7/24/2021"
output: pdf_document
---

# In this draft: 
* do not get rid of rows with NA weight or BMI.

* lots of code dedicated to looking at baseline windows

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
```

## Source code for demographic, death, enrollment, and dispensing read-in
```{r}
source_rmd("Data_Read_In_Before_Vitals_Table.rmd")
```

At this point, we are left with 4435 distinct patients who are dispensed GLP1a, have enrollment info, and have 72+ weeks between first dispense date and end of enrollment.

## Read in vital table
```{r warning = F, message = F}
ehr_vital = read_csv("Excel_Data/PATH_JING_LUO_VITAL_2020_03_31.csv")
ehr_vital
ehr_vital %>% distinct(STUDY_ID)
```

971,891 rows, 14590 distinct patients in vital table.

```{r}
colSums(is.na(ehr_vital))
```

### Convert MEASURE_DATE to a date
```{r}
ehr_vital$MEASURE_DATE = as.Date(ehr_vital$MEASURE_DATE, "%m/%d/%Y")
```

### Are any patients missing all of their WT and BMI values?
```{r}
NA_wt_bmi = ehr_vital %>% group_by(STUDY_ID) %>% 
  summarise(nWT = sum(!is.na(WT)), 
  nBMI = sum(!is.na(ORIGINAL_BMI))) %>%
  filter(nWT == 0 & nBMI == 0) 

# convert column values of STUDY_ID in NA_wt_bmi to a vector
NA_wt_bmi_IDs = as.vector(NA_wt_bmi[['STUDY_ID']]); NA_wt_bmi_IDs

# filter out IDs that are in NA_wt_bmi_IDs
ehr_vital1 = ehr_vital %>% filter(!(STUDY_ID %in% NA_wt_bmi_IDs) ); ehr_vital1

ehr_vital1 %>% distinct(STUDY_ID)
```
Eliminated 45 patients when filtering out patients who had missing WTs and BMIs for all of their rows. 

Now there are 14545 patients in the vital table. 

## NOTE: There will be some rows that are missing both WT and BMI. But another row for the same STUDY_ID and MEASURE_DATE will include WT and/or BMI. 

```{r}
colSums(is.na(ehr_vital1))
```
Remove RAW_VITAL_SOURCE since it's missing for every row

```{r}
ehr_vital1 = ehr_vital1 %>% select(-RAW_VITAL_SOURCE)
```

```{r}
View(ehr_vital1 %>% arrange(STUDY_ID, MEASURE_DATE)) 
```

For the same patient and same MEASURE_DATE, WT & BMI measures are mutually exclusive with Smoking & Tobacco info. 



### Bother later with consolidating smoking/tobacco stuff with wt/bmi stuff from same measure date ###

## Join disp_enroll4 with ehr_vital1
```{r}
disp_enroll_vitals = left_join(disp_enroll4, ehr_vital1, by = "STUDY_ID"); disp_enroll_vitals
```

## Check out NA values
```{r}
colSums(is.na(disp_enroll_vitals))
```
Lots of NA but we won't be so focused on getting rid of variables and observations this time, as they will be filtered out anyway when looking at certain analyses.

## Do this again after the left join: 
### Are any patients missing all of their WT and BMI values?
Important to do after the left join because all the STUDY_IDs from disp_enroll stay in the df even if they would have been eliminated earlier in the 45 eliminations from vital table. 

```{r}
NA_wt_bmi_2 = disp_enroll_vitals %>% group_by(STUDY_ID) %>% 
  summarise(nWT = sum(!is.na(WT)), 
  nBMI = sum(!is.na(ORIGINAL_BMI))) %>%
  filter(nWT == 0 & nBMI == 0) 

# convert column values of STUDY_ID in NA_wt_bmi_2 to a vector
NA_wt_bmi_IDs_2 = as.vector(NA_wt_bmi_2[['STUDY_ID']]); NA_wt_bmi_IDs_2

# check that NA_wt_bmi_IDs_2 contain NA for all body metrics
disp_enroll_vitals %>% filter((STUDY_ID %in% NA_wt_bmi_IDs_2) ) %>% select(STUDY_ID, HT, WT, ORIGINAL_BMI) %>% View()

# filter out IDs that are in NA_wt_bmi_IDs_2
disp_enroll_vitals1 = disp_enroll_vitals %>% filter(!(STUDY_ID %in% NA_wt_bmi_IDs_2) ); disp_enroll_vitals1

disp_enroll_vitals1 %>% distinct(STUDY_ID)
```

```{r}
disp_enroll_vitals1 %>% nrow()
distinct(disp_enroll_vitals1) %>% nrow()


disp_enroll_vitals2 = distinct(disp_enroll_vitals1); disp_enroll_vitals2 %>% group_by(STUDY_ID)
```

4426 distinct patients with 
- dispensed a GLP1a
- have enrollment info
- 72+ weeks between first dispensement and end of enrollment
- have *some* vital info (at least one WT and/or BMI on record)

## Rows that have a valid WT
```{r}
disp_enroll_vitals2 %>% filter(!is.na(WT))
```
4424 distinct patients with 
- dispensed a GLP1a
- have enrollment info
- 72+ weeks between first dispensement and end of enrollment
- have at least one WT on record

## A closer look at 4426 vs 4424 (at least one WT and/or BMI *versus* at least one WT)
```{r}
setdiff_IDs = setdiff(disp_enroll_vitals2 %>% distinct(STUDY_ID), disp_enroll_vitals2 %>% filter(!is.na(WT)) %>% distinct(STUDY_ID) ); setdiff_IDs

# convert column values of STUDY_ID in setdiff_IDs to a vector
setdiff_IDs = as.vector(setdiff_IDs[['STUDY_ID']]); setdiff_IDs

disp_enroll_vitals2 %>% filter(STUDY_ID %in% setdiff_IDs) %>% select(STUDY_ID, HT, WT, ORIGINAL_BMI)
```
2 patients who are missing HT & WT for ALL their rows but have AT LEAST ONE BMI 

## Rows that have a BMI but are missing WT
```{r}
disp_enroll_vitals2 %>% filter(is.na(WT) & !is.na(ORIGINAL_BMI)) %>% select(STUDY_ID, WT, ORIGINAL_BMI, HT)
```
2018 patients have at least one row that is missing WT but has BMI

## How many rows that have a BMI but are missing WT also have a HT (That we can calculate WT with)?
```{r}
disp_enroll_vitals2 %>% filter(is.na(WT) & !is.na(ORIGINAL_BMI) & !is.na(HT)) %>% select(STUDY_ID, WT, ORIGINAL_BMI, HT)
```
* look into calculating WT for these 176 patients thru their valid BMI and HT *

## Rows that have both WT and BMI
```{r}
disp_enroll_vitals2 %>% filter(!is.na(WT) & !is.na(ORIGINAL_BMI))


colSums(is.na(disp_enroll_vitals2 %>% filter(!is.na(WT) & !is.na(ORIGINAL_BMI))))
```
4420 patients have at least one row that contains both their WT and BMI
Reaffirming that rows that have complete WT & BMI are mutually exclusive with rows that have complete SMOKING/TOBACCO/TOBACCO_TYPE

## Rows that have neither WT nor BMI
```{r}
disp_enroll_vitals2 %>% filter(is.na(WT) & is.na(ORIGINAL_BMI))
```
4416 patients have at least one row that is missing both their WT and BMI (but these rows are kept as they can provide SMOKING info) 

## Flag unusual/potentially erroneous WTs and BMIs
```{r}
disp_enroll_vitals3 = disp_enroll_vitals2 %>%
  mutate(
    below70WT = ifelse(WT < 70, 1, 0),
    above700WT = ifelse(WT > 700, 1, 0),
    below15BMI = ifelse(ORIGINAL_BMI < 15, 1, 0),
    above90BMI = ifelse(ORIGINAL_BMI > 90, 1, 0)
    )

disp_enroll_vitals3
```

## Flag MEASURE_DATES that are between weeks (0 , 68])
## Also flag MEASURE_DATEs that are between weeks (-8,0]
```{r}
disp_enroll_vitals3 = disp_enroll_vitals3 %>% mutate(
  measBetween0_68 = ifelse(MEASURE_DATE > firstDispDate & MEASURE_DATE <= firstDispPlus68W, 1, 0),
  measBetweenN8_0 = ifelse(MEASURE_DATE > firstDispDate - weeks(8) & MEASURE_DATE <= firstDispDate, 1, 0)
)

disp_enroll_vitals3 %>% select(STUDY_ID, firstDispDate, MEASURE_DATE , measBetween0_68, measBetweenN8_0) %>% distinct()
```

## Be mindful to also apply the condition of !is.na(WT) (some MEASURE_DATEs have a missing WT but are still in dataset b/c might contain BMI and/or smoking)
```{r}
disp_enroll_vitals3 %>% filter(
  measBetween0_68 == 1 & !is.na(WT)
)

disp_enroll_vitals3 %>% filter(
  measBetweenN8_0 == 1 & !is.na(WT)
)

```

If we only include people who have at least one wt in (-8,0] AND at least one wt in (0,68], we would have at most 2527 patients. 

## Patients with at least one wt in (-8, 0] and at least one wt in (0,68]
```{r}
intersect(disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>% 
            distinct(STUDY_ID), 
          disp_enroll_vitals3 %>% filter(measBetweenN8_0 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
There are 2486 patients who have at least one wt in (-8,0] AND at least one wt in (0,68]. 


## How many of the 4424 have 1+ body measures between week (0,72]?
```{r}
disp_enroll_vitals3 %>% filter(MEASURE_DATE > firstDispDate & MEASURE_DATE <= firstDispDate + weeks(72) & !is.na(WT))
```
3946 patients have 1+ body measures between week (0,72].


## Trying out new baseline intervals
## First: follow-up window upper bound @ 68 weeks
Get a count of patients who have a measure in each of the following windows:

* (-8, 2]

* (-12, 2]

* (-16, 2]

* (-20, 2]

* (-24, 2]


And then:

* (-8, 0]   ## already found to be 2527/4424

* (-12, 0]

* (-16, 0]

* (-20, 0]

* (-24, 0]

### also do all of these intersections with (0, 68]

## (-8,2]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(8) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
)
```
2672 patients have 1+ body measures between weeks (-8,2].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(8) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```

2631 patients have 1+ body measure between weeks (-8, 2] AND (0, 68]


## (-12,2]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(12) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
)
```
2875 patients have 1+ body measures between weeks (-12,2].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(12) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
2820 patients have 1+ body measure between weeks (-12, 2] AND (0, 68]

## (-16,2]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(16) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
)
```

3011 patients have 1+ body measures between weeks (-16,2].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(16) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
2949 patients have 1+ body measure between weeks (-16, 2] AND (0, 68]


## (-20,2]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(20) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
)
```

3106 patients have 1+ body measures between weeks (-20,2].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(20) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
3034 patients have 1+ body measure between weeks (-20, 2] AND (0, 68]


## (-24,2]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(24) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
)
```

3187 patients have 1+ body measures between weeks (-24,2].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(24) & MEASURE_DATE <= firstDispDate + weeks(2) & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
3106 patients have 1+ body measure between weeks (-24, 2] AND (0, 68]

## (-8,0]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(8) & MEASURE_DATE <= firstDispDate & !is.na(WT)
)
```
2527 patients have 1+ body measures between weeks (-8,0].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(8) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
2486 patients have 1+ body measure between weeks (-8, 0] AND (0, 68]

## (-12,0]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(12) & MEASURE_DATE <= firstDispDate & !is.na(WT)
)
```

2771 patients have 1+ body measures between weeks (-12,0].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(12) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
2716 patients have 1+ body measure between weeks (-12, 0] AND (0, 68]

## (-16,0]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(16) & MEASURE_DATE <= firstDispDate & !is.na(WT)
)
```

2940 patients have 1+ body measures between weeks (-16,0].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(16) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
2878 patients have 1+ body measure between weeks (-16, 0] AND (0, 68]

## (-20,0]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(20) & MEASURE_DATE <= firstDispDate & !is.na(WT)
)
```

3047 patients have 1+ body measures between weeks (-20,0].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(20) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
2975 patients have 1+ body measure between weeks (-20, 0] AND (0, 68]

## (-24,0]
```{r}
disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(24) & MEASURE_DATE <= firstDispDate & !is.na(WT)
)
```
3133 patients have 1+ body measures between weeks (-24,0].

```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(24) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         disp_enroll_vitals3 %>% filter(measBetween0_68 == 1 & !is.na(WT)) %>%
            distinct(STUDY_ID))
```
3052 patients have 1+ body measure between weeks (-24, 0] AND (0, 68]

## Second: follow-up window upper bound @ 72 weeks
Get a count of patients who have a measure in each of the following windows:

* (-8, 0]   

* (-12, 0]

* (-16, 0]

* (-20, 0]

* (-24, 0]

### also do intersection with follow-up window (0, 72]

First, create an object for IDs that have 1+ wt in weeks (0,72]
```{r}
measBetween0_72_IDs = disp_enroll_vitals3 %>% filter(MEASURE_DATE > firstDispDate &
                                 MEASURE_DATE <= firstDispDate + weeks(72) &
                                 !is.na(WT)
                               ) %>% 
  distinct(STUDY_ID)
```

## (-8,0] AND (0, 72]
```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(8) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         measBetween0_72_IDs)
```
2487 patients have 1+ body measure between weeks (-8, 0] AND (0, 72]

## (-12,0] AND (0, 72]
```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(12) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         measBetween0_72_IDs)
```
2718 patients have 1+ body measure between weeks (-12, 0] AND (0, 72]

## (-16,0] AND (0, 72]
```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(16) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         measBetween0_72_IDs)
```
2880 patients have 1+ body measure between weeks (-16, 0] AND (0, 72]

## (-20,0] AND (0, 72]
```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(20) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         measBetween0_72_IDs)
```
2977 patients have 1+ body measure between weeks (-20, 0] AND (0, 72]

## (-24,0] AND (0, 72]
```{r}
intersect(disp_enroll_vitals3 %>% filter(
  MEASURE_DATE > firstDispDate - weeks(24) & MEASURE_DATE <= firstDispDate  & !is.na(WT)
) %>% distinct(STUDY_ID), 
         measBetween0_72_IDs)
```
3,056 patients have 1+ body measure between weeks (-24, 0] AND (0, 72]

# Table 1 for baseline characteristics

## Rudimentary table 1 attempt #1: July 26, 2021

In order to include drug, baseline WT, baseline ORIGINAL_BMI later on, we still need to 

(Look in lines 419 and beyond in DRAFT 6 for the first two)
* 	Accounting for measure_dates that have 2+ differing weights:Choose one random weight from the measure_date to represent

*	Only use first dispensed GLP1a in drug breakdown 

* define baseline WT and BMI per patient

```{r, message = F, warning = F}
library(table1)

tableOneVar = disp_enroll_vitals3 %>% select(SEX.f, RACE.f, RACE_WBO.f, HISPANIC_YN.f,AGE_ENROLLMENT_cat.f) %>% distinct()
```

```{r}
label(tableOneVar$SEX.f) = "Sex" 
label(tableOneVar$RACE.f) = "Race" 
label(tableOneVar$RACE_WBO.f) = "Race (White/Black/Other)"
label(tableOneVar$HISPANIC_YN.f) = "Hispanic"
label(tableOneVar$AGE_ENROLLMENT_cat.f) = "Age"

table1(~ SEX.f + RACE.f + RACE_WBO.f + HISPANIC_YN.f + AGE_ENROLLMENT_cat.f,  tableOneVar)
```

